%-------------------------
% Resume : Nathaniel Wetzel
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nathaniel Wetzel} \\ \vspace{1pt}
    \small 206-771-6504 $|$ \href{mailto:nnwetzel@icloud.com}{\underline{nnwetzel@icloud.com}} $|$ 
    \href{https://www.linkedin.com/in/nnwetzel/}{\underline{linkedin.com/in/nnwetzel}} $|$
    \href{https://github.com/nnwetzel}{\underline{github.com/nnwetzel}}
\end{center}

\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}First-year Computer Science student at Northeastern University, Boston. AFE Scholarship recipient. Upcoming Amazon summer intern (2024). Adept at problem-solving and eager to learn new technologies. Committed to increasing Southeast Asian STEM representation, given my half-Vietnamese heritage.} \\
    }
 \end{itemize}

%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Present -- May 2027}
      {Computer Science}{Boston, MA}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Related Courses}{: Fundamentals of Computer Science 1 (IP), Discrete Structures (IP)} \\
     \textbf{Activities}{: Huskiers and Outing Club}
    }}
 \end{itemize}
 \resumeSubheading
      {Ballard High School}{Sept. 2019 -- June 2023}
      {GED}{Seattle, WA}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Honors}{: 4.3/4.0 GPA, 1500 (730 EBRW, 770 Math) SAT Score, Amazon Future Engineer Scholarship, Elks Most Valuable Student Scholarship, AP Scholar with Honors} \\
     \textbf{Activities}{: FIRST Robotics, Varsity Cross Country, National Honors Society}
    }}
 \end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon}{July 2022 -- July 2022}
      {Extern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Acquired technical competencies in programming, AWS, IoT, and cloud computing}
        \resumeItem{Learned about Amazon culture, how to succeed in a corporate environment, and various roles/career paths in the tech industry}
        \resumeItem{Nominated to present final project to peers, Seattle Public School staff, and a panel of Amazon software engineers (audience of 100). Awarded certificate of excellence (one of four recipients out of 15 presenters)}
      \resumeItemListEnd
  
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Google Student Developer Club}{Sep. 2022 -- Jun. 2023}
      {Committee}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Fostered a sense of community and belonging among club members}
        \resumeItem{Assisted peers in overcoming programming challenges and debugging issues}
    \resumeItemListEnd

    \resumeSubheading
      {Kidd Valley}{June 2021 -- Aug. 2023}
      {Server}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Took customer orders, delivered them to tables, prepared beverages, and managed cash transactions to guarantee an enjoyable dining experience for patrons}
        \resumeItem{Collaborated with team members to ensure smooth restaurant operations, adapting to fast-paced work environments, while maintaining a high standard of service and efficiency}
        \
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{TextExcel} $|$ \emph{Java}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a text-based spreadsheet software using Java}
            \resumeItem{Implemented a user-friendly command-line interface for creating, editing, and managing spreadsheets}
            \resumeItem{Included built-in help guide and arithmetic formula capabilities for single cells and cell ranges}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Ratchet} \\
     \textbf{Developer Tools}{: Git, VS Code, jGRASP} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
